Sulfur Dioxide on Water's Surface

### 2011-06-28 Conclusions.tex
Not much

Having now examined this passageway of \suldiox~from the gas to adsorbed aqueous phases, we may now turn to further filling in the details of adsorption and interfacial chemistry of gas molecules. What species form during the adsorption transition, and how do molecular properties affect the process? Can we form a theory that will more fully explain the transit of many small molecules of environmental and industrial interest? This study is one of several aiming to characterize \suldiox~adsorption and behavior on aqueous surfaces. We plan to report further results of computational simulation and experimental studies regarding temperature and chemical constituent effects on atmospherically relevant water surfaces.

>>>>

Having now examined this passageway of \suldiox~from the gas to adsorbed aqueous phases, we may turn to further filling in the details of adsorption and interfacial chemistry of gas molecules. What species form during the adsorption transition, and how do molecular properties affect the process? Can we form a theory that will more fully explain the transit of many small molecules of environmental and industrial interest? This study is one of several aiming to characterize \suldiox~adsorption and behavior on aqueous surfaces. We plan to report further results of ongoing computational simulation and experimental studies regarding temperature and chemical constituent effects on atmospherically relevant water surfaces.
